Depth over distance: Hawaiian cryptic reef communities are more distinct across ~90 m depth than ~2500 km of shallow habitat

### 2023-11-08 manuscript.Rmd
updates

>>>>

Despite the fact that shallow ARMS units were deployed within a narrow depth range (8--17 m), depth still emerged as a significant driver of community variation. Depth in and of itself does not affect anything [[cite?]]{.mark}, but at the same time, the factors that are known to covary most consistently with it (viz. temparature and light) do not show much variation across such a narrow range. However, we also did not sample these values for the specific depths where units where deployed. So, depth is clearly doing something. We only have environmental data from units deployed \< 30 m, but community ordinations show that there are considerable differences between all the shallow units across the entire span of the archipelago and the $\geq$ 30 m units collected from a single island.
